---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Jiwon Choi
  - Kevin Roe
thanks: "Code and data are available at: [https://github.com/jwonc4602/2024_US_Election_Forecast](https://github.com/jwonc4602/2024_US_Election_Forecast)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```


# Introduction



Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....




# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement
	
Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.



Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it. 

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.



# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.  

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.


### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```




# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point {#sec-second-point}

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point {#sec-third-point}

## Implications {#sec-implications}

## Weaknesses and Next Steps {#sec-weaknesses}

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {#sec-appendix}

# Pollster Methodology Analysis {#sec-appendix-pollster}

# Idealized Methodology {#sec-appendix-methodology}

Because the US operates on the Electoral College system, where state-affiliation matters, I would use Stratified Random Sampling to ensure each state is represented proportionally in the survey, improving accuracy and representativeness. My target population would be voter-eligible citizens in the United States who are above 18 years old. My sampling frame will use voter registration databases that are stratified by key demographics (age, race, gender, geographic region, income, and education level). Finally for my potential sample size, I will aim for around 10,000 respondents to ensure a reasonable margin of error, but I expect the actual sample to be less. 

I would primarily recruit respondents using online methods such as surveys on social media platforms like Facebook and Instagram to reach younger audiences and use interactive voice response systems on the phone to reach older or less tech-savvy demographics. 

To ensure the data aggregated are valid, I would make sure to cross-check responses with voter registration databases and implement various logic checks within the survey to detect inconsistent answers. For example, if a survey respondent claims to have already voted but stated they’re unlikely to vote makes the data response unreliable. 

The biggest concern with online surveys is to handle non-response bias. To mitigate this, I will make sure to over-sample underrepresented groups and use multiple attempts to contact individuals online or run weekly polls. By running frequent surveys, I will make sure to aggregate results using a moving average in the summary results dashboard to smooth out short-term fluctuations. I will also make sure to develop checks online to prevent someone from filling out the form more than once or track the different people we called to ensure we do not have duplicate entries. Finally, because the United States does not run elections using a popular vote, I will weight the survey results to reflect the US voting population based on US Census data and voter turnout estimates, while also factoring demographic factors such as race, gender, and age. 

[NTD: ADD MORE DETAILS ABOUT METHODOLOGY]
To allocate the \$100,000 budget, I would budget \$20,000 for a survey platform subscription to handle a large amount of data. I would put \$50,000 into advertising and recruitment for targeted digital ads and phone surveys. I will also use \$20,000 for data analysts and poll aggregation services and \$10,000 for re-contact surveys, contingency costs, and other miscellaneous costs. However, I believe \$100,000 is on the lower end to ensure a high-quality poll and will most likely cost more. Regardless, most of the costs will come from collecting the data, and I have budgeted for this reality (ADD CITATION). 

[NTD: ADD THIS AS ANOTHER SECTION]
Please find the proposed question list for the online survey attached here (INSERT URL).

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```



\newpage


# References


